Brief Announcement: Tight Bounds for Online Balanced Repartitioning

### 2020-03-27 paper/paper.tex
Rewrite

\begin{theorem}
  No deterministic algorithm for BRP with two clusters can achieve a competitive ratio smaller than $2k-1$.
\end{theorem}

@@

For any sequence of paging requests, we produce a corresponding BRP pairwise request sequence.
To this end, fix an algorithm ALG for the paging problem.
When a request to element $e$ comes, we identify the set $S \in \{ A,B,C \}$ that contains the corresponding node $v_e$.
Then, the adversary forms a component $S$, and dismisses it right after the algorithm collocates the whole $S$ on one cluster.
Recall that forming a component means that the adversary continuously issues requests to any two nodes of a component that are split.

@@

OPT observes the actions of the algorithm LFD (Least Forward Distance) for the caching problem, and performs adequate reconfigurations within feasible configurations described in the previous paragraph.
Precisely, if LFD chooses to evict the element $e$ from the cache, OPT chooses the configuration with the corresponding node $v_e$ split, and pays $2\alpha$ for it.

The well-known property of LFD is that it pays $1$ only after $\mathbb{C}$ different pages are revealed to the algorithm, where $\mathbb{C}$ is the size of its cache.
In our case, $\mathbb{C} = 2k-1$, and hence the algorithm pays at least $2\alpha$ for each (transformed to BRP) paging request, and OPT pays $2\alpha$ every $2k-1$ paging requests.
Hence, the claim holds.
\end{proof}

>>>>

\begin{theorem}
  No deterministic algorithm for BRP with two clusters can achieve a competitive ratio smaller than $2k-1$.

  \maciek{better formulation below}
  Fix any $k$. If there exists a $\gamma$-competitive \ldots (SIDMA)
\end{theorem}

@@

For any sequence of paging requests $I_{PAGE}$, we produce a corresponding BRP pairwise request sequence $I_{BRP}$.
To this end, fix an algorithm ALG for the paging problem.
When a request to element $e$ comes, we identify the set $S \in \{ A,B,C \}$ that contains the corresponding node $v_e$.
Then, the adversary forms a component $S$, and dismisses it right after the algorithm collocates the whole $S$ on one cluster.
Recall that forming a component means that the adversary continuously issues requests to any two nodes of a component that are split.

@@

Finally, we describe the actions of OPT on the input sequence $I_{BRP}$.
OPT observes the actions of the algorithm LFD (Least Forward Distance for the caching problem) on $I_{PAGE}$, and performs corresponding actions within its feasible configurations.
Precisely, if LFD chooses to evict the element $e$ from the cache, OPT chooses the configuration with the corresponding node $v_e$ split.
The cost of OPT is then $2\alpha \cdot LFD$.

It is well-known that LFD is an optimal algorithm for paging, and any deterministic algorithm for paging with cache size $2k-1$ is at least $2k-1$-competitive.

TODO: rewrite the conclusion in the similar way to sidma paper
\end{proof}
